A Gentle Introduction into Structural Causal Models

### 2021-04-22 paper/draft.Rmd
prediction and criteria section

@@

>>>>

Note that prediction in a causal model and prediction in a machine learning context are not the same thing.
In prediction in causal models we can only modify root nodes.
We are unable to modify the child nodes in causal prediction.
Meanwhile, in a machine learning context we can modify any variable.
We do not have a underlying causal specification, henceforth we are able to modify any variable and undertake prediction. 
One should note that clearly the prediction in causal models has more explanatory power than the prediction in a vanilla-machine learning model.

@@

## Criteria

## D-Seperation

### Markovian Condition

#### In Graphical Model

#### in SCM

### Backdoor criteria

```{tikz, backdoor, fig.cap ="Backdoor Criterion",  fig.align="center", echo =F}
\usetikzlibrary{calc}
\usetikzlibrary{positioning}
\usetikzlibrary{arrows}
  \begin{tikzpicture}[
    sharp corners=2pt,
    inner sep=7pt,
    node distance=3cm,
    >=latex]
\tikzstyle{my node}=[draw, shape = circle, minimum height=1cm,minimum width=1cm]
\node[my node, fill=gray!30] (A){A};
\node[my node, fill=gray!30] at ($(A)!0.5!(A)-(0pt,1.5cm)$) (T) {T};
\node[my node,right of=T, fill=gray!30](C){C};
\draw[->] (A) -- (T);
\draw[->] (A) -- (C);
\draw[->] (T) -- (C);
\end{tikzpicture}
```
